\chapter{Team Plan}
\label{sec:plan}

At beginning of the year, we proposed three possible plans of action
to our liaisons:

\begin{enumerate}

\item \emph{Viable Solution and Initial Integration}

  This would be the scenario where we had found a viable solution
  early enough in the academic year such that we would have had the
  time to both fully develop a final solution and to begin exploring
  how we would be able to integrate our solution into the current Ceph
  system. In this scenario, we would have found a viable solution
  sometime early in the fall semester. This would be after exploring a
  number of possible solutions and documenting why they were
  unsatisfactory. Our Midyear Report would contain details about what
  options we had explored, why they were unsatisfactory and a detailed
  explanation of what our solution was. It would also contain a proof
  that details why our solution is, theoretically, correct.

  The spring semester would be dedicated to creating a simulation data
  center that we could use to model an implementation of our
  solution. We would use a cluster of desktop machines or Raspberry
  Pis to simulate our solution to ensure that the constants on the
  runtime of our algorithm were not so large as to make our solution
  impossible to implement in real life. Finally, we would begin to
  look at the Ceph code base and see how we might be able to make
  recommendations about how to integrate our solution into Ceph's
  system. Our Final Report would contain a final description of all of
  the work done over the course of the school year, including the
  description of the solutions we considered, the reasons why those
  solutions were dismissed, the final solution and a proof of its
  correctness, a description of a simulation of the solution, and
  recommendations for how to incorporate the solution into the current
  Ceph system.


\item \emph{Viable Solution and Proof of Concept}

  This would be the case where we had found a viable solution later in
  the school year. While it would depend on when we finalized the
  solution, our Midyear Report would contain details about the
  algorithms that we had considered up to that point and a discussion
  about the drawbacks of the ones we discarded. Depending on when we
  had found a viable algorithm, we may have included in that document
  a description of the algorithm and a proof of the correctness of that
  algorithm.

  The spring semester would be about proving that our solution is
  viable. We would create the proof of correctness, if we hadn't
  already done it in the fall semester and we would create and run the
  simulations of our algorithm on an imitation cluster. Our Final
  Report would contain a final description of all of the work done
  over the course of the school year, including the description of the
  solutions we considered, the reasons why those solutions were
  dismissed, the final solution, a proof of its correctness and a
  description of a simulation of the solution.


\item \emph{In-Depth Exploration of Ideas}

  The last scenario was the case where we are unable to find a
  solution. In that case, our goal would be to lay as much groundwork
  as we could for a future clinic team to take over after we
  finish. In the fall semester, we would do a significant amount of
  research into related work. We would try to apply the related work
  to come up with a solution and we would discuss all of the options
  that we considered and found were unsatisfactory. Our midyear report
  would contain all of the insights we gleaned over the semester,
  including the possible solutions that we explored and the reasons we
  decided they were unsatisfactory.

  In the spring semester, we would spend most of our time working on
  possible solutions, since we had spent most of the previous semester
  doing research. Our goal would be to come up with as many algorithms
  as we could and analyze the pros and cons of each of them. The Final
  Report would be devoted to describing the different algorithms and
  pieces of related work that we looked at over the year. We would
  also provide details into why the solutions that we looked at were
  unsatisfactory. The goal would be to create a document that provides
  a future clinic team with a good foundation to take up this project
  after us.

\end{enumerate}

We completed the goals of the second plan. 
