\chapter{Commonly Used Terms}
\label{sec:terms}

\section{General terms}
\begin{itemize}

\item Cluster: Computers that are networked together to perform a
  common task. A Ceph cluster is a single deployment of the Ceph file
  system across a group of computers.
    
\item Clock Drift: The natural drift over time that a computer clock
  experiences.
    
\item Clock Wander: The rate of clock drift.

\item Consistency: The partial ordering of events to preserve the
  causal relationships between them.
    
\item Node: A single computer in a cluster.
  
\item Node Failure: When a node in the cluster becomes unavailable,
  either temporarily or permanently.
      
\item Node Freeze: A hold on processing all writes that are sent to
  that node. Reads may continue to be processed.
    
\item Node Time: The time that the clock on a particular node reads;
  it is not guaranteed to be the same as real time, although we hope
  it is close.
    
\item Out-of-Band Communication: Communication between users of a Ceph
  cluster that Ceph has no way of detecting or recording.
    
\item Real Time: The true, global time of the cluster. This can be
  considered the time advertised by a standards organization or a
  perfect clock.

\item Snapshot: A consistent recording of the entire state of a Ceph
  cluster.  This includes the state of files and objects stored within
  the cluster.
    
\item Strong Consistency: Ceph is strongly consistent. It requires
  that ordering of events be maintained even in the face of
  out-of-band communication. It also requires that data stored in the
  cluster will be returned correctly when asked for or be
  unavailable. It does not allow data to be returned corrupt.

\item Time Synchronization Protocol: A protocol that the nodes in a
  cluster implement to synchronize their clocks as they drift.


  
\end{itemize}

\section{Ceph specific terms}

\begin{itemize}

\item Heartbeat: A message sent between nodes for the purpose of
  checking that the recipient is still alive. If a node does not
  respond to a set number of heartbeats, that node is marked as failed
  and a new map is generated.

\item Map: A data structure that associates file hashes with
  clients. With the current map, a client may communicate directly
  with the Ceph node most relevant to a given transaction. A new map
  is generated, and lazily propagated to nodes and clients, each time
  the availability of nodes changes.
  	
\item Object Storage Device (OSD): A single storage unit. Functionally
  equivalent to a single computer or node.

\item Placement Group (PG): Objects stored in a Ceph cluster are
  aggregated into Placement Groups by a distributed hash
  function. Each Object Storage Device contains a large number of
  Placement Groups.
   
\item Reliable Autonomic Distributed Object Store (RADOS): The core
  services and software backing the Ceph file system.

\end{itemize}
